\begin{MainPart}

  \color{Black}
  \MainTitle{\ColorHighlight}{\ColorTextMain}{About me}{\faUser}
  \vspace{0.25cm}
  {
    \begin{flushleft}
      Dynamic and enthusiastic student looking for a professionalization contract to gain strong knowledge and capabilities. I am particularly interested in functional programming, as I am currently learning Scala. I plan to continue learning effects frameworks such as Cats Effect and ZIO, or big data processing frameworks like Spark.
    \end{flushleft}
  }
  %%% Education
  \MainTitle{\ColorHighlight}{\ColorTextMain}{Education}{\faGraduationCap}
  \Experience%
  {\ColorHighlight}
  {\href{https://www.polytech.umontpellier.fr/images/ecole/Plaquettes/SPECIALITE_IG_2018_EN.pdf}{Engineering degree in Computer Science}}
  {\href{https://english.polytech.umontpellier.fr/}{Polytech Montpellier, France}}
  {2021 --- 2024}
  {
    Polytech Montpellier is a French engineering school at Montpellier, France.\\
    This degree is equivalent to a Master's degree

    \begin{multicols}{2}
      Major in Computer Science
      \begin{ItemList}{\ColorHighlight}
        \item [\ding{226}] Algorithms
        \item [\ding{226}] Software engineering
        \item [\ding{226}] Mathematics (Algebra, Statistics)
      \end{ItemList}
      \columnbreak%
      Minor in Management
      \begin{ItemList}{\ColorHighlight}
        \item [\ding{226}] Cost analysis
        \item [\ding{226}] Project management
        \item [\ding{226}] Budgetary control
      \end{ItemList}
    \end{multicols}
  }
  \Experience%
  {\ColorHighlight}
  {Preparatory classes}
  {\href{https://www.umontpellier.fr/en/}{Montpellier University of Science, France}}
  {2019 --- 2021}
  {
    A 2-year course leading to one of Polytech's highly selective engineering schools, with Mathematics and Physics as majors and Computer Science and Chemistry as minors.
  }

  %%% Experiences 
  \MainTitle{\ColorHighlight}{\ColorTextMain}{Experience}{\faSuitcase}
  \Experience%
  {\ColorHighlight}
  {Assistant Software Engineer}
  {Teads France}
  {Jun. 2022 --- Aug. 2022}
  {
    I worked in an agile workflow on both the back-end and front-end on the new demo console application. I learned about pure functional programming in Scala with the Cats Effect framework, and UI testing with React and Cypress. I handled every feature from start to finish (coding, testing, deployment, maintenance). By the end of the internship, the back-end was fully functional, as was the front-end.
  }
  \Experience%
  {\ColorHighlight}
  {Intern}
  {L'Avion Jaune}
  {Jun. 2020}
  {
    L'Avion Jaune is a cartography company located in Hérault, in the south of France. They use light aircrafts to map sites. This internship was my first job experience: I had to develop a web application to automate flight reports. It allowed me to gain a better understanding of web languages and Python.
  }
\end{MainPart}